Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{{DISTRIBUTION STATEMENT A. Approved for public release.} }

### 2021-05-13 paper/example.tex
Updates from Overleaf

The system implementation is cyber-hardened by automatically transforming the model to insert high-assurance components in the form of a filter and a monitor as shown in \figref{fig:hardened}(a). A filter enforces an invariant over each datum in the data stream by not forwarding input to its output if that input is violating. The auto-generated AGREE specification states that only well-formed inputs are passed to the output. The system designer must provide this filtering policy, but it is usually based on the existing assumptions made by downstream components that consume the filter output.

@@

The high-assurance components are automatically synthesized from the AGREE specifications to equivalent models in the CakeML language. CakeML itself provides a complete verified compilation to binaries for several different platforms meaning that the resulting binaries exactly preserve the meaning of the original CakeML code \cite{cakeml}.

>>>>

The system implementation is cyber-hardened using BriefCASE, which automatically transforms the model by inserting high-assurance components in the form of a filter and a monitor as shown in \figref{fig:hardened}(a). A filter enforces an invariant over each datum in the data stream by not forwarding input to its output if that input is violating. The auto-generated AGREE specification states that only well-formed inputs are passed to the output. The system designer must provide this filtering policy, but it is usually based on the existing assumptions made by downstream components that consume the filter output.

@@

The high-assurance components are automatically synthesized by SPLAT from the AGREE specifications to equivalent models in the CakeML language. CakeML itself provides a complete verified compilation to binaries for several different platforms meaning that the resulting binaries exactly preserve the meaning of the original CakeML code \cite{cakeml}.

### 2021-05-13 paper/synthesis.tex
Updates from Overleaf

\paragraph{Initialization}
A monitor may need to make a certain minimum number of observations before being able to make a meaningful assessment of behavior. Until that threshold is attained, the monitor is essentially in a kind of \emph{initialization}. In order for correct code to be generated, monitor specifications need to spell out the values of output ports when in such initialization phases. For example, suppose a monitor does some kind of differential assessment of inputs at adjacent timeslices, alerting when (say) the measured location of a UAV at time $t$ and $t+1$ is such that the distance between the two locations is unusually large. Such a monitor needs two measurements before making its first judgement, but at the time of its first output, only one measurement will have been made. The specification for this monitor has to explicitly say what the correct first output is.

>>>>

\paragraph{Initialization}
A monitor may need to accumulate a certain minimum number of observations before being able to make a meaningful assessment of behavior. Until that threshold is attained, the monitor is essentially in a kind of \emph{initialization} phase. In order for correct code to be generated, monitor specifications need to spell out the values of output ports when in such initialization phases. For example, suppose a monitor does some kind of differential assessment of inputs at adjacent timeslices, alerting when (say) the measured location of a UAV at times $t$ and $t+1$ is such that the distance between the two locations is unusually large. Such a monitor needs two measurements before making its first judgement, but at the time of its first output, only one measurement will have been made. The specification has to explicitly say what the correct first output is.
